An Extension of LTL with Rules\\ and its Application to Runtime Verification

### 2019-02-07 rule-ltl.tex
Updates from Overleaf

\section{RV for past-time
first-order  LTL and its Extension}
\label{EPLTLRV}

@@

We then have to add
following updates between steps 3 and 4 of the above algorithm, when performing runtime verification of
$\psi$.

\noindent \begin{description}
\item For each $r_j ( x_j ) = \varphi_j ( x_j )$:
\item{\ \ }  calculate $\current ( \varphi_j )$;
\item{\ \ }  $\current ( r_j )  := \current (\varphi_j)$;
\item{\ \ } $\current ( r_j ( y ) )$ := $\rename ( r_j(x_j) ,  y )$;
\item{\ \ } $\current ( r_j ( a ) )$ := if $\current ( r_j ) ( a )$
then $\btrue$ else $\bfalse$
\end{description}

@@

\noindent
As in the propositional case, the evaluation order cannot be
simply top down or bottom up, since relations can appear
both on the left and the right of a definition
such as $r ( x ) := p ( x ) \vee \ominus r ( x )$. For that,
we need to use the mixed evaluation order, described in Section~\ref{LTLruntime}.

>>>>

\section{RV for Past-Time
First-Order  LTL and its Extension}
\label{EPLTLRV}

@@

We then have to add
following updates to step~4 of the above algorithm, when performing runtime verification of
$\psi$.

\noindent \begin{description}
\item For each rule 
$r_j ( x_j ) := \varphi_j ( x_j )$:
\item{\ \ }  calculate $\current ( \varphi_j )$;
\item{\ \ }  $\current ( r_j )  := \current (\varphi_j)$;
\item{\ \ } $\current ( r_j ( y ) )$ := $\rename ( r_j(x_j) ,  y )$;
\item{\ \ } $\current ( r_j ( a ) )$ := if $\current ( r_j ) ( a )$
then $\btrue$ else $\bfalse$
\end{description}

@@

\noindent
As in the propositional case, the evaluation order cannot be
simply top down or bottom up, since relations can appear
both on the left and the right of a definition
such as $r ( x ) := p ( x ) \vee \ominus r ( x )$. For that,
we need to use the {\em mixed} evaluation order, described in Section~\ref{LTLruntime}.
